Computation and comparison of the stable northeastern United States marine boundary layer

### 2020-12-08 Paper/results.tex
More fixes from Mike Sprague

To determine the appropriate mesh size and resolution, a grid study
was conducted using the stable 5 m/s ABL case and the Nalu-Wind code.
A number of cases were set up using the surface roughness and
prescribed temperature decreases listed in Table
\ref{tab:z0tempparam}, but with varying grid resolutions and
conservative estimates for the domain size required.  As shown in
table \ref{tab:GridStudySetup}, the horizontal resolutions varied from
10 m to 2.5 m cells for the coarse and fine cases, respectively.  All
simulations for the grid study also used a vertical resolution of
dz=2.5 m and the same vertical extent of 1 km.

@@

After running each case for 15,000 s, the boundary layer
statistics and horizontally averaged profiles were averaged for
another 5,000 s.  In Table \ref{tab:CompareAMRvsNalu}, some mean
statistics are given for both cases, including the friction velocity
$u_\tau$, the turbulence intensity TI at z=20 m, and local shear
exponent $\alpha$ at z=20 m, defined as
$$ \alpha = \frac{z}{U_{horiz}} \frac{d U_{horiz}}{dz}.
$$ AMR-Wind and Nalu-Wind produced nearly identical values for the
TI=0.048, which is close to measured target of 4.5\%, and similar
agreement was found for the shear exponent $\alpha$.  A minor
descrepancy was found in the friction velocity $u_\tau$, with AMR-Wind
resulting in a value slightly lower than Nalu-Wind.

The comparison of the horizontally averaged wind profiles is shown in
Figure  \ref{fig:CompareAMRvsNaluWind_WSDir}.  At the forcing height
z=20 m, the wind speed and wind shear are close to an exact match
between the two LES codes.  The horizontal wind speeds continue to
agree well for $z < 100$ m, beyond which a relatively constant velocity
difference is observed.   For both AMR-Wind and Nalu-Wind, an
approximately linear veer profile was observed until $z\approx$ 250 m,
at which point the wind direction remained constant until the
inversion layer height.

@@

%%%%%%%%%%% Compare Nalu/AMR WS/WDir profiles %%%%%%%%%%%%%%%%%%%%%%%
% Postprocessing/ABLStats/AMRWind_NaluWind_stable_05ms_mesh2_5x2_5x2_5_paper.ipynb
\begin{figure} %[hbt!]
  \centering
  \includegraphics[width=2.5in]{figures/Compare_AMRWind_NaluWind/AMRWind_NaluWind_stable_05ms_mesh2p5_2p5_2p5_WS.png}
  \includegraphics[width=2.5in]{figures/Compare_AMRWind_NaluWind/AMRWind_NaluWind_stable_05ms_mesh2p5_2p5_2p5_Wdir.png}\\
  \caption{\label{fig:CompareAMRvsNaluWind_WSDir} Comparison of
    AMR-Wind and Nalu-Wind horizontal velocity and wind direction
    profiles for the stable 5 m/s boundary layer. The dashed
    horizontal line corresponds to the measurement height z=20 m. }
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%% Compare Nalu/AMR TI/Temp profiles %%%%%%%%%%%%%%%%%%%%%%
% Postprocessing/ABLStats/AMRWind_NaluWind_stable_05ms_mesh2_5x2_5x2_5_paper.ipynb
\begin{figure} [hbt!]
  \centering
  \includegraphics[width=2.5in]{figures/Compare_AMRWind_NaluWind/AMRWind_NaluWind_stable_05ms_mesh2p5_2p5_2p5_TI.png}
  \includegraphics[width=2.5in]{figures/Compare_AMRWind_NaluWind/AMRWind_NaluWind_stable_05ms_mesh2p5_2p5_2p5_T.png}
  \caption{\label{fig:CompareAMRvsNaluWind_TTI} Comparison of AMR-Wind
    and Nalu-Wind turbulence intensity and temperature profiles for
    the stable 5 m/s boundary layer. The dashed horizontal line
    corresponds to the measurement height z=20 m.}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

  \caption{\label{fig:CompareAMRvsNaluSpectra} Comparison of AMR-Wind
    and Nalu-Wind wind spectra at z=20 m for the stable 5 m/s boundary
    layer. }
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

The qualitative behavior of the stable boundary layers can be seen
through snapshots of the flow taken from each of the simulations.  In
Figure \ref{fig:SnapshotsZ20}, instantaneous snapshots of the
horizontal and vertical velocities for each of the three cases at the
z=20 m measurement height are shown.  The largest difference can be
seen in the size of the flow structures between the very unstable and
stable cases.  Longer streaks are evident in the 15 m/s case compared
to the 5 m/s and 15 m/s cases, which is consistent with the nearly
50\% larger integral length scale $L$ given in Table
\ref{tab:CompareAMRallWS}.  The differences in the vertical velocity
are also evident in Figure  \ref{fig:SnapshotsZ20}.  At higher wind speeds the
magnitude of the vertical $w'$ fluctuations increase, which plays a
strong role in the growth of the boundary layer.

@@

  \end{tikzpicture}
  \caption{ \label{fig:SnapshotsZ20} Snapshots of the horizontal
    velocity and vertical velocity, taken at $t$=20,000 s of the
    simulations at height z=20 m, for the AMR-Wind calculation of the
    stable 5 m/s, 10 m/s, and 15 m/s ABL. }
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%% stable WS profiles %%%%%%%%%%%%%%%%%%%%%%%%%
% Created in Postprocessing/ABLStats/AMRWind_NaluWind_stable_AllWS_2p5Cubed.ipynb
\begin{figure}[hbt!]
  \centering
  \includegraphics[width=2.5in]{figures/AMRWind_allWS/AMRWind_stable_WS.png}
  \includegraphics[width=2.5in]{figures/AMRWind_allWS/AMRWind_stable_WDir.png}
  \caption{ \label{fig:CompareAMRallWS} Comparison of the horizontal
    wind speed and wind direction profile for the stable 5 m/s, 10
    m/s, and 15 m/s boundary layers. The dashed horizontal line
    corresponds to the measurement height z=20 m.}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%% stable WS profiles %%%%%%%%%%%%%%%%%%%%%%%%%
% Created in Postprocessing/ABLStats/AMRWind_NaluWind_stable_AllWS_2p5Cubed.ipynb
\begin{figure}[hbt!]
  \centering
  \includegraphics[width=2.5in]{figures/AMRWind_allWS/AMRWind_stable_TI.png}
  \includegraphics[width=2.5in]{figures/AMRWind_allWS/AMRWind_stable_T.png}
  \caption{ \label{fig:CompareAMRallTTI} Comparison of the turbulence
    intensity and temperature profile for the stable 5 m/s, 10 m/s,
    and 15 m/s boundary layers. The dashed horizontal line corresponds
    to the measurement height z=20 m.}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

To determine the appropriate mesh size and resolution, a grid study
was conducted using the stable 5 m/s ABL case and the Nalu-Wind code.
A number of cases were set up using the surface roughness and
prescribed temperature decreases listed in Table
\ref{tab:z0tempparam}, but with varying grid resolutions and
conservative estimates for the domain size required.  As shown in
table \ref{tab:GridStudySetup}, the horizontal resolutions varied from
10 m to 2.5 m cells for the coarse and fine cases, respectively.  All
simulations for the grid study also used a vertical resolution of
$\Delta_z$=2.5 m and the same vertical extent of 1 km.

@@

After running each case for 15,000 s, the boundary layer
statistics and horizontally averaged profiles were averaged for
another 5,000 s.  In Table \ref{tab:CompareAMRvsNalu}, some mean
statistics are given for both cases, including the friction velocity
$u_\tau$, the turbulence intensity TI at $z$=20 m, and local shear
exponent $\alpha$ at $z$=20 m, defined as
$$ \alpha = \frac{z}{U_{horiz}} \frac{d U_{horiz}}{dz}.
$$ AMR-Wind and Nalu-Wind produced nearly identical values for the
TI=0.048, which is close to measured target of 4.5\%, and similar
agreement was found for the shear exponent $\alpha$.  A minor
descrepancy was found in the friction velocity $u_\tau$, with AMR-Wind
resulting in a value slightly lower than Nalu-Wind.

The comparison of the horizontally averaged wind profiles is shown in
Figure  \ref{fig:CompareAMRvsNaluWind_WSDir}.  At the forcing height
$z$=20 m, the wind speed and wind shear are close to an exact match
between the two LES codes.  The horizontal wind speeds continue to
agree well for $z < 100$ m, beyond which a relatively constant velocity
difference is observed.   For both AMR-Wind and Nalu-Wind, an
approximately linear veer profile was observed until $z\approx$ 250 m,
at which point the wind direction remained constant until the
inversion layer height.
The level of agreement between AMR-Wind and Nalu-Wind at the higher
elevations is comparable to the inter-comparison of LES simulations
Beare et al.~\cite{Beare2006}, and may be improved through finer scale
simulations which fully resolve the lateral turbulent lengthscales.

@@

%%%%%%%%%%% Compare Nalu/AMR WS/WDir profiles %%%%%%%%%%%%%%%%%%%%%%%
% Postprocessing/ABLStats/AMRWind_NaluWind_stable_05ms_mesh2_5x2_5x2_5_paper.ipynb
\begin{figure} %[hbt!]
  \centering
  \includegraphics[width=2.5in]{figures/Compare_AMRWind_NaluWind/AMRWind_NaluWind_stable_05ms_mesh2p5_2p5_2p5_WS.png}
  \includegraphics[width=2.5in]{figures/Compare_AMRWind_NaluWind/AMRWind_NaluWind_stable_05ms_mesh2p5_2p5_2p5_Wdir.png}\\
  \caption{\label{fig:CompareAMRvsNaluWind_WSDir} Comparison of
    AMR-Wind and Nalu-Wind horizontal velocity and wind direction
    profiles for the stable 5 m/s boundary layer. The dashed
    horizontal line corresponds to the measurement height $z$=20 m. }
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%% Compare Nalu/AMR TI/Temp profiles %%%%%%%%%%%%%%%%%%%%%%
% Postprocessing/ABLStats/AMRWind_NaluWind_stable_05ms_mesh2_5x2_5x2_5_paper.ipynb
\begin{figure} [hbt!]
  \centering
  \includegraphics[width=2.5in]{figures/Compare_AMRWind_NaluWind/AMRWind_NaluWind_stable_05ms_mesh2p5_2p5_2p5_TI.png}
  \includegraphics[width=2.5in]{figures/Compare_AMRWind_NaluWind/AMRWind_NaluWind_stable_05ms_mesh2p5_2p5_2p5_T.png}
  \caption{\label{fig:CompareAMRvsNaluWind_TTI} Comparison of AMR-Wind
    and Nalu-Wind turbulence intensity and temperature profiles for
    the stable 5 m/s boundary layer. The dashed horizontal line
    corresponds to the measurement height $z$=20 m.}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

  \caption{\label{fig:CompareAMRvsNaluSpectra} Comparison of AMR-Wind
    and Nalu-Wind wind spectra at $z$=20 m for the stable 5 m/s boundary
    layer. }
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

The qualitative behavior of the stable boundary layers can be seen
through snapshots of the flow taken from each of the simulations.  In
Figure \ref{fig:SnapshotsZ20}, instantaneous snapshots of the
horizontal and vertical velocities for each of the three cases at the
$z$=20 m measurement height are shown.  The largest difference can be
seen in the size of the flow structures between the very unstable and
stable cases.  Longer streaks are evident in the 15 m/s case compared
to the 5 m/s and 15 m/s cases, which is consistent with the nearly
50\% larger integral length scale $L$ given in Table
\ref{tab:CompareAMRallWS}.  The differences in the vertical velocity
are also evident in Figure  \ref{fig:SnapshotsZ20}.  At higher wind speeds the
magnitude of the vertical $w'$ fluctuations increase, which plays a
strong role in the growth of the boundary layer.

@@

  \end{tikzpicture}
  \caption{ \label{fig:SnapshotsZ20} Snapshots of the horizontal
    velocity and vertical velocity, taken at $t$=20,000 s of the
    simulations at height $z$=20 m, for the AMR-Wind calculation of the
    stable 5 m/s, 10 m/s, and 15 m/s ABL. }
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%% stable WS profiles %%%%%%%%%%%%%%%%%%%%%%%%%
% Created in Postprocessing/ABLStats/AMRWind_NaluWind_stable_AllWS_2p5Cubed.ipynb
\begin{figure}[hbt!]
  \centering
  \includegraphics[width=2.5in]{figures/AMRWind_allWS/AMRWind_stable_WS.png}
  \includegraphics[width=2.5in]{figures/AMRWind_allWS/AMRWind_stable_WDir.png}
  \caption{ \label{fig:CompareAMRallWS} Comparison of the horizontal
    wind speed and wind direction profile for the stable 5 m/s, 10
    m/s, and 15 m/s boundary layers. The dashed horizontal line
    corresponds to the measurement height $z$=20 m.}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%% stable WS profiles %%%%%%%%%%%%%%%%%%%%%%%%%
% Created in Postprocessing/ABLStats/AMRWind_NaluWind_stable_AllWS_2p5Cubed.ipynb
\begin{figure}[hbt!]
  \centering
  \includegraphics[width=2.5in]{figures/AMRWind_allWS/AMRWind_stable_TI.png}
  \includegraphics[width=2.5in]{figures/AMRWind_allWS/AMRWind_stable_T.png}
  \caption{ \label{fig:CompareAMRallTTI} Comparison of the turbulence
    intensity and temperature profile for the stable 5 m/s, 10 m/s,
    and 15 m/s boundary layers. The dashed horizontal line corresponds
    to the measurement height $z$=20 m.}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
